### 2016-05-13 Paper/Paper.tex
Paper progress

\documentclass[a4paper, 12pt]{article}
\usepackage{comment} % enables the use of multi-line comments (\ifx \fi) 
\usepackage{lipsum} %This package just generates Lorem Ipsum filler text. 
\usepackage{fullpage} % changes the margin
\usepackage{cite}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{amsfonts}
\usepackage{float}
\linespread{1.15}
\graphicspath{ {images/} }

@@

\begin{wrapfigure}{R}{0.7\textwidth}%this figure will be at the right
  \centering
  \includegraphics[width=0.7\textwidth]{induced}
   \caption{\label{inducedfig} From \cite{seis_induced}. Count of M $\geq3$ earthquakes in the central and eastern United States from 1973 to April 2015. Two abrupt increases in the earthquake rate occurred in 2009 and 2013. Red dots represent earthquakes that occurred between 2009 and April 2015, and blue dots represent earthquakes that occurred between 1973 and 2008. Prior to 2009, earthquakes were spread across the United States. Beginning in 2009 the earthquakes are tightly clustered in a few areas}. 
\end{wrapfigure}

@@

\subsection{Fuzzy c-Means Clustering}\label{fuzz}.
So that this paper can be self contained, I include an introduction to Fuzzy c-Means clustering and related concepts. This section will consist of an introduction to clustering followed by the way in which it is applied to this work.

@@

\section{Results}
These are some of the results

\begin{wrapfigure}{R}{0.5\textwidth}%this figure will be at the right
  \centering
  \includegraphics[width=0.5\textwidth]{clusters}
  \caption{\label{clusters} Results of the Fuzzy c-Means clustering on the data sample}. 
\end{wrapfigure}

\begin{wrapfigure}{L}{0.5\textwidth}%this figure will be at the right
   \centering
  \includegraphics[width=0.5\textwidth]{k_means_sil}
   \caption{\label{k_means_sil} ... }. 
\end{wrapfigure}

\section{Discussion and Analysis}

@@

\end{thebibliography}
\end{document}

>>>>

\documentclass[letterpaper, 12pt]{article}
\usepackage{comment} % enables the use of multi-line comments (\ifx \fi) 
\usepackage{lipsum} %This package just generates Lorem Ipsum filler text. 
\usepackage{fullpage} % changes the margin
\usepackage{cite}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{amsfonts}
\usepackage{float}

\linespread{1.15}
\graphicspath{ {images/} }

@@

\begin{figure}[H]%this figure will be at the right
  \centering
  \includegraphics[width=0.7\textwidth]{induced}
   \caption{\label{inducedfig} From \cite{seis_induced}. Count of M $\geq3$ earthquakes in the central and eastern United States from 1973 to April 2015. Two abrupt increases in the earthquake rate occurred in 2009 and 2013. Red dots represent earthquakes that occurred between 2009 and April 2015, and blue dots represent earthquakes that occurred between 1973 and 2008. Prior to 2009, earthquakes were spread across the United States. Beginning in 2009 the earthquakes are tightly clustered in a few areas.}
\end{figure}

@@

\subsection{Fuzzy c-Means Clustering}\label{fuzz}
So that this paper can be self contained, I include an introduction to Fuzzy c-Means clustering and related concepts. This section will consist of an introduction to clustering followed by the way in which it is applied to this work.

@@

\section{Results}
Unfortunately, there are no deterministic algorithms that exist to compute the $k$ Fuzzy c-Means clusters from a set of $j$ vectors exactly. For that reason we apply the FPC algorithm cited in Section \ref{fuzz} to approximate the centers of the clustering analysis. Furthermore, since this algorithm requires a predefined $k$, we run the FPC algorithm for $k \in [5,11]$, as it is correct practice to reduce the dimensionality of the data set (in this case $k < 12$) when clustering the $j$ vectors around $k$ centers. Figures \ref{clusterfig} and \ref {k_means_sil} show the graphical results of the clusterings. For exact numerical results regarding the found cluster centers, see the tables in Appendix A.

\begin{figure}[H]
\centering
\caption{\label{clusterfig} Each Figure (a - e) shows the clusters resulting from the running of the FPC algorithm for unique values if $k$. These results actually occur in 9-dimensional space, so a 6 degree Principal Component Analysis was used to reduce the dimensionality of each vector to 3 so that they could be pictured in these figures. For this reason, some of the detail gets lost, but the clusters are all still decernable.}
\begin{tabular}{cc}
  \includegraphics[width=65mm]{k5} &   \includegraphics[width=65mm]{k6} \\
(a) $k = 5, FPC = 0.6667$ & (b) $k = 6, FPC = .8333$ \\[6pt]
 \includegraphics[width=65mm]{k7} &   \includegraphics[width=65mm]{k8} \\
(c) $k = 7, FPC = .8333$ & (d) $k = 8, FPC =  0.6667$ \\[6pt]
\end{tabular}
\end{figure}
\begin{figure}[H]
\centering
\begin{tabular}{cc}
 \includegraphics[width=65mm]{k9} &   \includegraphics[width=65mm]{k10} \\
(d) $k = 9, FPC = .6111$ & (e) $k = 10, FPC = 1$ \\[6pt]
\end{tabular}
\end{figure}

\begin{figure}[H]%this figure will be at the right
   \centering
   \caption{\label{k_means_sil} This is a silhouette plot evaluating the fit of the model to the data. It is a common method of evaluation used in addition to the FPC. This plot shows the silhouette values for each value of $k$. Note that the cluster values range from $[2,7]$. These are offset by $-3$ so a cluster value of 5 on the chart shows $k = 5 + 3 = 8$. In general, the closer the silhouette value is to 1, the better the fit of the model. }
  \includegraphics[width=0.75\textwidth]{k_means_sil}
\end{figure}

\section{Discussion and Analysis}
\subsubsection{Fuzzy c-Means Results}\label{fcmr}

We stopped at k = 10 because FPC became 1

There are a few silhouette values close to 1, we pick one with highest coefficent 
\subsubsection{Translating \ref{fcmr} to Insight on Saline Formations}

@@

\end{thebibliography}

\pagebreak
\section{Appendix A}
These tables compliment the results in Figure \ref{clusterfig}. The tables list the 9-dimensional coordinates of the centers approximated by each run of the Fuzzy c-Means clustering algorithm for $k \in [5,10]$. Note that these centers were originally 12 dimensions (one for each dimension of the feature vectors), but were dimensionally reduced with Principal Component Analysis to reduce the complexity of the computations without loss of generality.

\begin{table}[h]
\centering
\caption{9 dimensional coordinates of the centers found at each run of Fuzzy c-Means clustering.}
\label{tablecenters}
\begin{tabular}{lllllllll}
k = 5   & fpc =   & 0.6667  &         &         &         &         &         &         \\
0.0015  & -0.0025 & 0.0086  & -0.0107 & -0.0009 & 0.0066  & -0.0126 & 0.0017  & 0.0083  \\
-0.0107 & -0.0027 & -0.0038 & 0.0017  & 0.0092  & -0.0004 & 0.0225  & -0.0067 & 0.0081  \\
-0.0083 & 0.0084  & 0.0036  & -0.0016 & -0.0015 & 0.0086  & -0.0107 & -0.0009 & 0.0066  \\
-0.0052 & 0.0017  & 0.0083  & -0.0107 & -0.0027 & -0.0019 & 0.0017  & 0.0101  & 0.0007  \\
0.0224  & -0.0067 & 0.0081  & -0.0051 & 0.0085  & -0.0140 & 0.0036  & -0.0019 & 0.0086  \\
        &         &         &         &         &         &         &         &         \\
k = 6   & fpc =   & 0.8333  &         &         &         &         &         &         \\
-0.0006 & 0.0069  & 0.0027  & -0.0092 & 0.0071  & 0.0013  & -0.0035 & 0.0082  & 0.0026  \\
-0.0092 & 0.0065  & -0.0032 & 0.0082  & 0.0029  & 0.0086  & 0.0031  & -0.0015 & 0.0028  \\
-0.0007 & 0.0015  & 0.0098  & -0.0025 & 0.0077  & 0.0027  & -0.0092 & 0.0071  & 0.0013  \\
0.0009  & 0.0082  & 0.0026  & -0.0092 & 0.0065  & -0.0016 & 0.0082  & 0.0027  & 0.0089  \\
0.0029  & -0.0015 & 0.0030  & 0.0020  & 0.0019  & -0.0050 & 0.0007  & 0.0074  & 0.0027  \\
-0.0092 & 0.0071  & 0.0013  & -0.0039 & 0.0082  & 0.0026  & -0.0092 & 0.0065  & -0.0017 \\

        &         &         &         &         &         &         &         &         \\
k = 7   & fpc =   & 0.8333  &         &         &         &         &         &         \\
0.0015  & -0.0025 & 0.0086  & -0.0107 & -0.0009 & 0.0066  & -0.0126 & 0.0017  & 0.0083  \\
-0.0107 & -0.0027 & -0.0038 & 0.0017  & 0.0092  & -0.0004 & 0.0225  & -0.0067 & 0.0081  \\
-0.0083 & 0.0084  & 0.0036  & -0.0016 & -0.0015 & 0.0086  & -0.0107 & -0.0009 & 0.0066  \\
-0.0052 & 0.0017  & 0.0083  & -0.0107 & -0.0027 & -0.0019 & 0.0017  & 0.0101  & 0.0007  \\
0.0224  & -0.0067 & 0.0081  & -0.0051 & 0.0085  & -0.0140 & 0.0036  & -0.0019 & 0.0086  \\
-0.0107 & -0.0009 & 0.0066  & -0.0118 & 0.0017  & 0.0083  & -0.0107 & -0.0027 & -0.0024 \\
0.0017  & 0.0104  & -0.0021 & 0.0236  & -0.0063 & 0.0089  & -0.0049 & 0.0077  & -0.0126 \\
\end{tabular}
\end{table}
\begin{table}[]
\begin{tabular}{lllllllll}
k = 8   & fpc =   & 0.6667  &         &         &         &         &         &         \\
-0.0006 & 0.0069  & 0.0027  & -0.0092 & 0.0071  & 0.0013  & -0.0035 & 0.0082  & 0.0026  \\
-0.0092 & 0.0065  & -0.0032 & 0.0082  & 0.0029  & 0.0086  & 0.0031  & -0.0015 & 0.0028  \\
-0.0007 & 0.0015  & 0.0098  & -0.0025 & 0.0077  & 0.0027  & -0.0092 & 0.0071  & 0.0013  \\
0.0009  & 0.0082  & 0.0026  & -0.0092 & 0.0065  & -0.0016 & 0.0082  & 0.0027  & 0.0089  \\
0.0029  & -0.0015 & 0.0030  & 0.0020  & 0.0019  & -0.0050 & 0.0007  & 0.0074  & 0.0027  \\
-0.0092 & 0.0071  & 0.0013  & -0.0039 & 0.0082  & 0.0026  & -0.0092 & 0.0065  & -0.0017 \\
0.0082  & 0.0030  & 0.0072  & 0.0044  & -0.0011 & 0.0042  & 0.0022  & 0.0010  & -0.0047 \\
0.0011  & 0.0081  & 0.0035  & -0.0086 & 0.0067  & 0.0013  & -0.0041 & 0.0079  & 0.0026  \\
        &         &         &         &         &         &         &         &         \\
k = 9   & fpc =   & 0.6111  &         &         &         &         &         &         \\
0.0015  & -0.0025 & 0.0086  & -0.0107 & -0.0009 & 0.0066  & -0.0126 & 0.0017  & 0.0083  \\
-0.0107 & -0.0027 & -0.0038 & 0.0017  & 0.0092  & -0.0004 & 0.0225  & -0.0067 & 0.0081  \\
-0.0083 & 0.0084  & 0.0036  & -0.0016 & -0.0015 & 0.0086  & -0.0107 & -0.0009 & 0.0066  \\
-0.0052 & 0.0017  & 0.0083  & -0.0107 & -0.0027 & -0.0019 & 0.0017  & 0.0101  & 0.0007  \\
0.0224  & -0.0067 & 0.0081  & -0.0051 & 0.0085  & -0.0140 & 0.0036  & -0.0019 & 0.0086  \\
-0.0107 & -0.0009 & 0.0066  & -0.0118 & 0.0017  & 0.0083  & -0.0107 & -0.0027 & -0.0024 \\
0.0017  & 0.0104  & -0.0021 & 0.0236  & -0.0063 & 0.0089  & -0.0049 & 0.0077  & -0.0126 \\
0.0036  & -0.0011 & 0.0102  & -0.0106 & -0.0020 & 0.0066  & -0.0120 & -0.0001 & 0.0083  \\
-0.0107 & -0.0027 & -0.0028 & 0.0041  & 0.0099  & -0.0009 & 0.0222  & -0.0067 & 0.0084  \\
        &         &         &         &         &         &         &         &         \\
k = 10  & fpc=    & 1.0000  &         &         &         &         &         &         \\
-0.0005 & 0.0114  & 0.0039  & -0.0123 & 0.0122  & 0.0004  & 0.0172  & -0.0116 & 0.0040  \\
-0.0123 & 0.0108  & 0.0000  & -0.0116 & 0.0039  & 0.0150  & -0.0071 & -0.0053 & 0.0028  \\
0.0090  & 0.0013  & -0.0054 & -0.0014 & 0.0131  & 0.0039  & -0.0123 & 0.0122  & 0.0004  \\
-0.0006 & -0.0116 & 0.0039  & -0.0123 & 0.0108  & -0.0011 & -0.0116 & 0.0029  & 0.0158  \\
-0.0056 & -0.0053 & -0.0010 & 0.0130  & 0.0023  & 0.0137  & 0.0008  & 0.0125  & 0.0039  \\
-0.0123 & 0.0122  & 0.0004  & 0.0176  & -0.0116 & 0.0039  & -0.0123 & 0.0108  & -0.0013 \\
-0.0116 & 0.0033  & 0.0120  & -0.0063 & -0.0044 & 0.0003  & 0.0132  & 0.0007  & 0.0133  \\
-0.0013 & 0.0139  & 0.0047  & -0.0115 & 0.0113  & 0.0004  & 0.0170  & 0.0139  & 0.0039  \\
0.0108  & -0.0019 & -0.0087 & 0.0053  & 0.0122  & -0.0061 & -0.0053 & -0.0012 & 0.0108  \\
0.0015  & 0.0132  & 0.0003  & 0.0126  & 0.0039  & -0.0123 & 0.0122  & 0.0004  & 0.0138 
\end{tabular}
\end{table}
\end{document}
